Canopy leaf area of a mature evergreen *Eucalyptus* woodland does not respond to elevated atmospheric [CO~2~] but tracks water availability

### 2015-08-18 review1.Rmd
edit to response

@@

**We have done so in response to specific comments listed below.**

>>>>

**We are surprised that the reviewer considers our paper 'lengthy', as the word count of ca. 5500 words is more than 30% lower than the allowed length for Global Change Biology (8000 words).**

@@

**We have done so in response to specific comments listed below, and made more minor changes to increase clarity.**
